### 2016-01-27 Irregular-occ/Irregular-occ.tex
.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{natbib,twoopt}
\usepackage[breaklinks=true]{hyperref} %% to avoid \citeads line fills
\usepackage{arydshln}
\bibpunct{(}{)}{;}{a}{}{,} %% natbib format for A&A and ApJ
\makeatletter
\newcommandtwoopt{\citeads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citealp[#1][#2]{#3}}}
\newcommandtwoopt{\citepads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citep[#1][#2]{#3}}}
\newcommandtwoopt{\citetads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citet[#1][#2]{#3}}}
\newcommandtwoopt{\citeyearads}[3][][]%
{\href{http://adsabs.harvard.edu/abs/#3}
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citeyear[#1][#2]{#3}}}
\makeatother
\titlerunning{Predictions of stellar occultations by irregular satellites up to 2017}
\authorrunning{Gomes-Júnior et al.}

@@

The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}, while the residuals are presented in Fig \ref{Fig: residuals} for Himalia and Carme as representatives.

\begin{figure*}
\subfigure{\includegraphics[width=8.8cm]{figures/Himalia_resid.eps}   \label{Fig: residuals-Himalia}}
\subfigure{\includegraphics[width=8.8cm]{figures/Carme_resid.eps}  \label{Fig: residuals-Carme}}
\caption{Residuals in topocentric right ascension and declination of the numerical integration for Himalia and Carme. \label{Fig: residuals}}
\end{figure*}

@@

All the orbits determined for the satellites show satisfying residuals. %Yet, one of the satellites has a peculiar situation. Its small number of observations in our set means that its orbit is definitely loosely constrained. 
The residuals are lower than those obtained with JPL ephemeris, but the accuracy of an ephemeris decreases when we get further from the time of observations. The main risk of divergence over time comes from the possible absence of long-term effects when fitting to a short timespan of observations. If that were the case, our ephemeris would diverge too quickly to be of any use. JPL ephemerides are fitted over all the available observations. As a result, they will diverge less quickly than our own. Though they are no longer precise enough for our use, they remain a precious reference to identify whether our own model presents a quick divergence. We compared our ephemeris to the JPL for all the Jupiter satellites we fitted, until 2017. The divergence between 2015 and 2018 is at most 98 mas in $\Delta \alpha \cos \delta$ and 58 mas in $\Delta \delta$ for Himalia and 181 mas in $\Delta \alpha \cos \delta$ and 152 mas in $\Delta \delta$ for Carme. A example of this difference for satellites Himalia and Carme over time is presented in Figure \ref{Fig: JPL-STE}.

\begin{figure*}
\subfigure{\includegraphics[width=8.8cm]{figures/JPL_DEC_Himalia.eps}    \label{Fig: JPL-STE-Himalia}}
\subfigure{\includegraphics[width=8.8cm]{figures/JPL_DEC_Carme.eps}  \label{Fig: JPL-STE-Carme}}
\caption{Geocentric right ascension and declination differences between the JUP300 JPL ephemeris and the special-tailored ephemeris for Himalia and Carme. \label{Fig: JPL-STE}}
\end{figure*}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{natbib,twoopt}
\usepackage[breaklinks=true, draft]{hyperref} %% to avoid \citeads line fills
\usepackage{arydshln}
\bibpunct{(}{)}{;}{a}{}{,} %% natbib format for A&A and ApJ
\makeatletter
\newcommandtwoopt{\citeads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citealp[#1][#2]{#3}}}
\newcommandtwoopt{\citepads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citep[#1][#2]{#3}}}
\newcommandtwoopt{\citetads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citet[#1][#2]{#3}}}
\newcommandtwoopt{\citeyearads}[3][][]%
{\href{http://adsabs.harvard.edu/abs/#3}
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citeyear[#1][#2]{#3}}}
\makeatother
\titlerunning{Predictions of stellar occultations by irregular satellites up to 2017}
\authorrunning{Gomes-Júnior et al.}

@@

The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}.%, while the residuals are presented in Fig \ref{Fig: residuals} for Himalia and Carme as representatives.

%\begin{figure*}
%\subfigure{\includegraphics[width=8.8cm]{figures/Himalia_resid.eps}   \label{Fig: residuals-Himalia}}
%\subfigure{\includegraphics[width=8.8cm]{figures/Carme_resid.eps}  \label{Fig: residuals-Carme}}
%\caption{Residuals in topocentric right ascension and declination of the numerical integration for Himalia and Carme. \label{Fig: residuals}}
%\end{figure*}

@@

All the orbits determined for the satellites show satisfying residuals. %Yet, one of the satellites has a peculiar situation. Its small number of observations in our set means that its orbit is definitely loosely constrained. 
The residuals are lower than those obtained with JPL ephemeris, but the accuracy of an ephemeris decreases when we get further from the time of observations. The main risk of divergence over time comes from the possible absence of long-term effects when fitting to a short timespan of observations. If that were the case, our ephemeris would diverge too quickly to be of any use. JPL ephemerides are fitted over all the available observations. As a result, they will diverge less quickly than our own. Though they are no longer precise enough for our use, they remain a precious reference to identify whether our own model presents a quick divergence.

We compared our ephemeris to the JPL for all the Jupiter satellites we fitted, until 2017. For instance, the divergence between 2015 and 2018 is at most 98 mas in $\Delta \alpha \cos \delta$ and 58 mas in $\Delta \delta$ for Himalia and 181 mas in $\Delta \alpha \cos \delta$ and 152 mas in $\Delta \delta$ for Carme.

In Fig. \ref{Fig: JPL-STE} it is presented the offsets of the positions published by \cite{GomesJunior2015} in declination relative to our ephemeris, to \cite{Jacobson2012} JUP300 JPL ephemeris and \cite{Emelyanov2008} ephemeris. It is possible to see that the systematic error point out by \cite{GomesJunior2015} is reduced with our ephemeris, as expected.

\begin{figure}
\includegraphics[width=8.8cm]{figures/Carme_ephemeris.eps} 
\caption{Offsets in declination of the positions published by \cite{GomesJunior2015} for Carme. The red "x" relative to the special-tailored ephemeris, the blue "+" relative to the JUP300 JPL ephemeris and the green dot relative to \cite{Emelyanov2008}. \label{Fig: JPL-STE}}
\end{figure}

%\begin{figure*}
%\subfigure{\includegraphics[width=8.8cm]{figures/JPL_DEC_Himalia.eps}    \label{Fig: JPL-STE-Himalia}}
%\subfigure{\includegraphics[width=8.8cm]{figures/JPL_DEC_Carme.eps}  \label{Fig: JPL-STE-Carme}}
%\caption{Geocentric right ascension and declination differences between the JUP300 JPL ephemeris and the special-tailored ephemeris for Himalia and Carme. \label{Fig: JPL-STE}}
%\end{figure*}

@@

\begin{figure*}
\begin{centering}
\subfigure[NEP081 JPL and \cite{Emelyanov2015} ephemeris]{\includegraphics[width=8.8cm]{figures/JPL-EME_Triton.eps} \label{Fig:offxtanomxjpl}}
\subfigure[\cite{Zhang2013} and \cite{Emelyanov2015} ephemeris]{\includegraphics[width=8.8cm]{figures/Zhang-EME.eps} \label{Fig:offxtanomxni}}
\caption{Comparison between the ephemeris between the \cite{Emelyanov2015}, \cite{Zhang2013} and JPL ephemeris.}
\label{Fig:offxanom}
\end{centering}
\end{figure*}
